Visual inference for networks

### 2016-02-09 paper/network-inference.Rnw

%% indicate IEEE Member or Student Member in form indicated below
\author{Samantha Tyner, Heike Hofmann \textit{Member, IEEE}}
\authorfooter{
%% insert punctuation at end of each item
\item
 Roy G. Biv is with Starbucks Research. E-mail: roy.g.biv@aol.com.
\item
 Ed Grimley is with Grimley Widgets, Inc.. E-mail: ed.grimley@aol.com.
\item
 Martha Stewart is with Martha Stewart Enterprises at Microsoft
 Research. E-mail: martha.stewart@marthastewart.com.
}

@@

\begin{enumerate}
\item Need to complete lineups in 2-3 weeks
\item Lineups: 
  \begin{enumerate}
  \item What sizes? 3, 6, 9, 12
  \item What data? Football, olga's data, teenage friends data?
  \item Other things to consider: coloring of nodes? 
  \end{enumerate}
\item Get simulated networds from models from RSiena
\item Figure out another way to fit a model and then simulate from it? 
\end{enumerate}

>>>>

%% indicate IEEE Member or Student Member in form indicated below
\author{Samantha Tyner, Heike Hofmann \textit{Member, IEEE}}
\authorfooter{
%% insert punctuation at end of each item
\item
 Samantha Tyner is with the Department of Statistics, Iowa State University. E-mail: sctyner@iastate.edu.
\item
 Heike Hofmann is with the Department of Statistics, Iowa State University. E-mail: hofmann@iastate.edu.
}

@@

\begin{enumerate}
\item Need to complete lineups in 2-3 weeks
\item Lineups: 
  \begin{enumerate}
  \item What sizes? 3, 6, 9, 12
  \item What data? Football, olga's data, teenage friends data?
  \item Other things to consider: coloring of nodes? 
  \item use replicates: different seeds for the same data produces different layouts -
  different draws from the model
  \end{enumerate}
\item Get simulated networds from models from RSiena
\item Figure out another way to fit a model and then simulate from it? 
\end{enumerate}
